---
title: "Lab 03 - Nobel laureates"
author: "Joseph Brudenell, Timi Ani, Myles Douglas, Caoimhe Nugent, Matthew Duncan"
date: "`r Sys.Date()`"
output: html_document
---


### Load packages and data

```{r load-packages, message = FALSE, warning=FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
nobel <- read_csv("data/nobel.csv")
```

### Exercise 1

#### Narrative

*There are 935 total entries within this data set, with a total of 26 variables. Each row represents a nobel prize winner, which includes all their necessary details for the data set*


### Exercise 2

#### Code

```{r nobel-living}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 3

#### Code

```{r facet-bar-plot}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 4

#### Code

```{r born-country-us}
# remove this comment and add your code here
```


### Exercise 5

#### Narrative

*Remove this text and add your answer here.*

#### Code

```{r facet-bar-plot-redo}
# remove this comment and add your code here
```


### Exercise 6

#### Code

```{r born-country}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*